---
title: "TS_FinalProject_Team2"
author: "Flora Huang, Zhangchi Liu, Qiansheng Zhou, Matt Zhang, Michael Wu"
date: '2022-05-23'
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(corrplot)
library(lubridate)
library(fpp)
library(TSA)
library(tseries)
library(Metrics)
```

## Data Exploratory

```{r}
# Load Data
df.raw <- read.csv(file = 'PRSA_Data_Wanshouxigong_20130301-20170228.csv')
head(df.raw, 10)
```

```{r}
# Check Missing Value
sapply(df.raw, function(x) sum(is.na(x)))
```

```{r}
# Check Correlation
df.num <- df.raw[,c(2:15, 17)]
res <- cor(as.matrix(df.num), method = "pearson", use = "pairwise.complete.obs")
res
```

```{r}
corrplot(res, type = "upper", order = "AOE", tl.col = "black", tl.srt = 40)
```

Select SO2, PM10, NO2, CO for further analysis

```{r}
df <- df.num[,c(1:11, 15)]
head(df)
```
## Feature Engineering

```{r}
df$date <- as.Date(with(df,paste(year,month,day,sep="-","%Y-%m-%d")))
Week <- as.Date(cut(df$date, "week"))
df_weekly <- data.frame(aggregate(PM2.5 ~ Week, df, mean))
df_weekly$PM10 <- aggregate(PM10 ~ Week, df, mean)[,c(2)]
df_weekly$SO2 <- aggregate(SO2 ~ Week, df, mean)[,c(2)]
df_weekly$NO2 <- aggregate(NO2 ~ Week, df, mean)[,c(2)]
df_weekly$CO <- aggregate(CO ~ Week, df, mean)[,c(2)]
df_weekly$TEMP <- aggregate(TEMP ~ Week, df, mean)[,c(2)]
df_weekly$O3 <- aggregate(O3 ~ Week, df, mean)[,c(2)]
df_weekly$WSPM <- aggregate(WSPM ~ Week, df, mean)[,c(2)]
head(df_weekly)
```

```{r}
# Check weekly correlation
res_weekly <- cor(as.matrix(df_weekly[,-1]), method = "pearson", use = "pairwise.complete.obs")
res_weekly

corrplot(res_weekly, type = "upper", order = "AOE", tl.col = "black", tl.srt = 40, addCoef.col = "black")
```
## PM2.5 Data Exploratory
```{r}
df_weekly$year = as.numeric(format(df_weekly$Week, format = "%Y"))
df_weekly$month = as.numeric(format(df_weekly$Week, format = "%m"))
df_weekly$day = as.numeric(format(df_weekly$Week, format = "%d"))

#df_weekly$MonthDay <- as.Date(paste(df_weekly$month, df_weekly$day, sep="-"), format = "%m-%d")
#df_weekly$MonthDay = as.Date(with(df_weekly,paste(month,day,sep="-","%m-%d")))
#df_weekly$MonthDay = as.Date(substr(df_weekly$Week, 6, 10), format = "%m%d")
# df_weekly$MonthDay = as.Date(substr(df_weekly$Week, 6, 10))
head(df_weekly)
```

```{r}
# ggplot(df_weekly) +
#   geom_line(aes(x = Week, y = PM2.5, color = year))
```

```{r}
# ggplot(data = df_weekly, aes(x = Week, y = PM2.5, group = year)) +       
#   geom_line(aes(group = year)) + geom_point()
```


```{r}
PM2.5_week = ts(df_weekly[,2], start = c(2013,9), end = c(2017,9), frequency = 52)

# split the data
train <- window(PM2.5_week, start = c(2013,9), end = c(2016,49))
test <- window(PM2.5_week, start = c(2016,50))
test
```
```{r}
head(df_weekly,1)
```


```{r}
PM10_week <- ts(df_weekly[,3], start = c(2013,9), end = c(2017,9), frequency = 52)
SO2_week <- ts(df_weekly[,4], start = c(2013,9), end = c(2017,9), frequency = 52)
NO2_week <- ts(df_weekly[,5], start = c(2013,9), end = c(2017,9), frequency = 52)
CO_week <- ts(df_weekly[,6], start = c(2013,9), end = c(2017,9), frequency = 52)
TEMP_week <- ts(df_weekly[,7], start = c(2013,9), end = c(2017,9), frequency = 52)
O3_week <- ts(df_weekly[,8], start = c(2013,9), end = c(2017,9), frequency = 52)
WSPM_week <- ts(df_weekly[,9], start = c(2013,9), end = c(2017,9), frequency = 52)

train_pm10 <- window(PM10_week, start = c(2013,9), end = c(2016,49))
test_pm10 <- window(PM10_week, start = c(2016,50))
train_so2 <- window(SO2_week, start = c(2013,9), end = c(2016,49))
test_so2 <- window(SO2_week, start = c(2016,50))
train_no2 <- window(NO2_week, start = c(2013,9), end = c(2016,49))
test_no2 <- window(NO2_week, start = c(2016,50))
train_co <- window(CO_week, start = c(2013,9), end = c(2016,49))
test_co <- window(CO_week, start = c(2016,50))
train_temp <- window(TEMP_week, start = c(2013,9), end = c(2016,49))
test_temp <- window(TEMP_week, start = c(2016,50))
train_o3 <- window(O3_week, start = c(2013,9), end = c(2016,49))
test_o3 <- window(O3_week, start = c(2016,50))
train_wspm <- window(WSPM_week, start = c(2013,9), end = c(2016,49))
test_wspm <- window(WSPM_week, start = c(2016,50))
```


```{r}
tsdisplay(train, main = "Plot of Training Weekly PM2.5 in Wanshouxigong")
```

```{r}
tsdisplay(log(train), main = "Plot of Log Training Weekly PM2.5 in Wanshouxigong")
```

## Box-Cox Transformation

```{r}
lambda = BoxCox.lambda(train)
lambda
```

```{r}
autoplot(train)
```

```{r}
train %>% BoxCox(lambda = lambda) %>% plot(main = 'Box-Cox Transformed PM2.5')
```

```{r}
train %>% BoxCox(lambda = 0) %>% plot(main = 'LogTransformed PM2.5')
```


```{r}
trans.PM <- BoxCox(train, lambda = lambda)
```

## Look for the differencing order
## original data test for stationary
```{r,warning=FALSE}
kpss.test(trans.PM)
adf.test(trans.PM)
kpss.test(train)
adf.test(train)
## the data without transformation is also stationary
```

<span style="color:blue">***Answer:The train data is stationary.The ACF plot decreases quickly to zero, which proves tat the data is stationary. The p value for KPSS test is  larger than 0.05 and the p value for ADF test is less than 0.05,  both proving that the train data is stationary.  No need to difference the data***  </span>


# seasonal differencing
```{r}
sea <- diff(train,lag=52)
tsdisplay(sea,main="Seasonal Differenced Train")
```

```{r}
tsdisplay(train, main = "Original Train")
```

```{r}
tsdisplay(trans.PM, main="Box Train") 
```

```{r}
tsdisplay(log(train),main = "Log(train)")
```
The data though looks having a seasonal pattern in the ACF

# 1. Arima model 
## a. Arima with transformation

###  • Model 1: # nonseasonal box trans
```{r}
m1 <- auto.arima(train,lambda = lambda,seasonal=FALSE)
summary(m1)
```

###  • Model 2: # nonseasonal log trans
```{r}
# nonseasonal log trans
m2<-auto.arima(train,lambda=0,seasonal=FALSE)
summary(m2)
```

###  • Model 3: # seasonal box trans
```{r}
# seasonal box trans
m3 <- auto.arima(train,lambda = lambda,seasonal = TRUE)
summary(m3)
```

###  • Model 4: # seasonal log trans
```{r}
# seasonal box trans
m4 <- auto.arima(train,lambda = 0,seasonal = TRUE)
summary(m4)
```

###  • Model 5: # seasonal box trans, D=1
```{r}
# seasonal box trans
m5 <- auto.arima(train,lambda = lambda,seasonal = TRUE,D=1)
summary(m5)
```

###  • Model 6: # seasonal log trans, D=1
```{r}
# seasonal box trans
m6 <- auto.arima(train,lambda = 0,seasonal = TRUE,D=1)
summary(m6)
```

## b. Arima without transformation

###  • Model 7: # nonseasonal
```{r}
m7 <- auto.arima(train,seasonal = FALSE)
summary(m7)
```

###  • Model 8: # seasonal
```{r}
m8 <- auto.arima(train,seasonal = TRUE)
summary(m8)
```

###  • Model 9: # seasonal, D=1
```{r}
m9 <- auto.arima(train,seasonal = TRUE,D=1)
summary(m9)
```

###  • Model 10: # seasonal naive
```{r}
m10 <- snaive(train, h=12) 
summary(m10)
```

## c. Forecast and Plots

```{r}
fore1 = forecast(m1, h = 12)
fore2 = forecast(m2, h = 12)
fore3 = forecast(m3, h = 12)
fore4 = forecast(m4, h = 12)
fore5 = forecast(m5, h = 12)
fore6 = forecast(m6, h = 12)
fore7 = forecast(m7, h = 12)
fore8 = forecast(m8, h = 12)
fore9 = forecast(m9, h = 12)
fore10 = forecast(m10, h = 12)
```

```{r}
plot(fore1)
plot(fore2)
plot(fore3)
plot(fore4)
plot(fore5)
plot(fore6)
plot(fore7)
plot(fore8)
plot(fore9)
plot(fore10)
```

### Nonseasonal Arima
```{r}
autoplot(train) +
  autolayer(test,series="actual test data")+
  autolayer(fore1$mean,series="ARIMA(3,0,0) with box")+
  autolayer(fore2$mean,series="ARIMA(3,0,0) with log")+  
  #autolayer(fore3$mean,series="ARIMA(3,0,0)(0,0,1)  with box ")+
  #autolayer(fore4$mean,series="ARIMA(3,0,0)(0,0,1)  with log")+
  #autolayer(fore5$mean,series="ARIMA(0,0,1)(1,1,0) with drift and box")+
  #autolayer(fore6$mean,series="ARIMA(0,0,1)(1,1,0) with drift and log")+ 
  autolayer(fore7$mean,series="ARIMA(4,0,0)")
  #autolayer(fore8$mean,series="ARIMA(5,0,0)(1,0,0)")+
  #autolayer(fore9$mean,series="ARIMA(0,0,1)(1,1,0)")+ 
  #autolayer(m10$mean, series="seasonal naive")
```

### Seasonal Arima without Seasonal Differencing
```{r}
autoplot(train) +
  autolayer(test,series="actual test data")+
  #autolayer(fore1$mean,series="ARIMA(3,0,0) with box")+
  #autolayer(fore2$mean,series="ARIMA(3,0,0) with log")+  
  autolayer(fore3$mean,series="ARIMA(3,0,0)(0,0,1)  with box ")+
  autolayer(fore4$mean,series="ARIMA(3,0,0)(0,0,1)  with log")+
  #autolayer(fore5$mean,series="ARIMA(0,0,1)(1,1,0) with drift and box")+
  #autolayer(fore6$mean,series="ARIMA(0,0,1)(1,1,0) with drift and log")+ 
  #autolayer(fore7$mean,series="ARIMA(4,0,0)")
  autolayer(fore8$mean,series="ARIMA(5,0,0)(1,0,0)")+
  #autolayer(fore9$mean,series="ARIMA(0,0,1)(1,1,0)")+ 
  autolayer(m10$mean, series="seasonal naive")
```

### Seasonal Arima with Seasonal Differencing
```{r}
autoplot(train) +
  autolayer(test,series="actual test data")+
  #autolayer(fore1$mean,series="ARIMA(3,0,0) with box")+
  #autolayer(fore2$mean,series="ARIMA(3,0,0) with log")+  
  #autolayer(fore3$mean,series="ARIMA(3,0,0)(0,0,1)  with box ")+
  #autolayer(fore4$mean,series="ARIMA(3,0,0)(0,0,1)  with log")+
  autolayer(fore5$mean,series="ARIMA(0,0,1)(1,1,0) with drift and box")+
  autolayer(fore6$mean,series="ARIMA(0,0,1)(1,1,0) with drift and log")+ 
  #autolayer(fore7$mean,series="ARIMA(4,0,0)")
  #autolayer(fore8$mean,series="ARIMA(5,0,0)(1,0,0)")+
  autolayer(fore9$mean,series="ARIMA(0,0,1)(1,1,0)")
  #autolayer(m10$mean, series="seasonal naive")
```

### Only test data
### Nonseasonal Arima

```{r}
autoplot(test,series="actual test data")+
  autolayer(fore1$mean,series="ARIMA(3,0,0) with box")+
  autolayer(fore2$mean,series="ARIMA(3,0,0) with log")+  
  #autolayer(fore3$mean,series="ARIMA(3,0,0)(0,0,1)  with box ")+
  #autolayer(fore4$mean,series="ARIMA(3,0,0)(0,0,1)  with log")+
  #autolayer(fore5$mean,series="ARIMA(0,0,1)(1,1,0) with drift and box")+
  #autolayer(fore6$mean,series="ARIMA(0,0,1)(1,1,0) with drift and log")+ 
  autolayer(fore7$mean,series="ARIMA(4,0,0)")
  #autolayer(fore8$mean,series="ARIMA(5,0,0)(1,0,0)")+
  #autolayer(fore9$mean,series="ARIMA(0,0,1)(1,1,0)")+ 
  #autolayer(m10$mean, series="seasonal naive")
```

### Seasonal Arima without Seasonal Differencing
```{r}
autoplot(test,series="actual test data")+
  #autolayer(fore1$mean,series="ARIMA(3,0,0) with box")+
  #autolayer(fore2$mean,series="ARIMA(3,0,0) with log")+  
  autolayer(fore3$mean,series="ARIMA(3,0,0)(0,0,1)  with box ")+
  autolayer(fore4$mean,series="ARIMA(3,0,0)(0,0,1)  with log")+
  #autolayer(fore5$mean,series="ARIMA(0,0,1)(1,1,0) with drift and box")+
  #autolayer(fore6$mean,series="ARIMA(0,0,1)(1,1,0) with drift and log")+ 
  #autolayer(fore7$mean,series="ARIMA(4,0,0)")
  autolayer(fore8$mean,series="ARIMA(5,0,0)(1,0,0)")+
  #autolayer(fore9$mean,series="ARIMA(0,0,1)(1,1,0)")+ 
  autolayer(m10$mean, series="seasonal naive")
```


### Seasonal Arima with Seasonal Differencing
```{r}
autoplot(test, series="actual test data")+
  #autolayer(fore1$mean,series="ARIMA(3,0,0) with box")+
  #autolayer(fore2$mean,series="ARIMA(3,0,0) with log")+  
  #autolayer(fore3$mean,series="ARIMA(3,0,0)(0,0,1)  with box ")+
  #autolayer(fore4$mean,series="ARIMA(3,0,0)(0,0,1)  with log")+
  autolayer(fore5$mean,series="ARIMA(0,0,1)(1,1,0) with drift and box")+
  autolayer(fore6$mean,series="ARIMA(0,0,1)(1,1,0) with drift and log")+ 
  #autolayer(fore7$mean,series="ARIMA(4,0,0)")
  #autolayer(fore8$mean,series="ARIMA(5,0,0)(1,0,0)")+
  autolayer(fore9$mean,series="ARIMA(0,0,1)(1,1,0)")
  #autolayer(m10$mean, series="seasonal naive")
```

## d. Metrics
```{r}
#Mean Absolute Percentage Error (MAPE)
mape1<-mape(test,fore1$mean)
mape2<-mape(test,fore2$mean)
mape3<-mape(test,fore3$mean)
mape4<-mape(test,fore4$mean)
mape5<-mape(test,fore5$mean)
mape6<-mape(test,fore6$mean)
mape7<-mape(test,fore7$mean)
mape8<-mape(test,fore8$mean)
mape9<-mape(test,fore9$mean)
mape10<-mape(test,fore10$mean)


#Mean Squared Error (MSE)
mse1<-mse(test,fore1$mean)
mse2<-mse(test,fore2$mean)
mse3<-mse(test,fore3$mean)
mse4<-mse(test,fore4$mean)
mse5<-mse(test,fore5$mean)
mse6<-mse(test,fore6$mean)
mse7<-mse(test,fore7$mean)
mse8<-mse(test,fore8$mean)
mse9<-mse(test,fore9$mean)
mse10<-mse(test,fore10$mean)

MAPE=c(mape1,mape2,mape3,mape4,mape5,mape6,mape7,mape8,mape9,mape10)
MSE=c(mse1,mse2,mse3,mse4,mse5,mse6,mse7,mse8,mse9,mse10)

model_name=c("ARIMA(3,0,0) ","ARIMA(3,0,0) ","ARIMA(3,0,0)(0,0,1) ","ARIMA(3,0,0)(0,0,1)","ARIMA(0,0,1)(1,1,0) with drift","ARIMA(0,0,1)(1,1,0) with drift","ARIMA(4,0,0)","ARIMA(5,0,0)(1,0,0)","ARIMA(0,0,1)(1,1,0)","Seasonal Naiive")
seadiff<-c(0,0,1,1,0,1,"NA")
lam<-c("2", "0", "2","0", "2","0","NA","NA","NA","NA")

results<-data.frame(model=model_name,Lambda=lam,AICc=c(m1$aicc,m2$aicc,m3$aicc,m4$aicc,m5$aicc,m6$aicc,m7$aicc,m8$aicc,m9$aicc,"NA"),BIC=c(m1$bic,m2$bic,m3$bic,m4$bic,m5$bic,m6$bic,m7$bic,m8$bic,m9$bic,"NA"),MAPE=MAPE,MSE=MSE)

results
```

# 2. Exponential Smoothing

```{r}
PM2.5_ES = ts(log(df_weekly$PM2.5), start = c(2013,9), end = c(2017,9), frequency = 52)
```




### split the data
```{r}
train_ES <- window(PM2.5_ES, start = c(2013,9), end = c(2016,47))
test_ES <- window(PM2.5_ES, start = c(2016,48), end =c(2017,9))
```

```{r}
tsdisplay(train_ES)
```

```{r}
plot(train_ES, main = "Plot of Daily log(PM2.5) in Wanshouxigong")
```

# decompose
```{r}
fit_add <- decompose(train_ES, type = 'additive')
plot(fit_add)
fit_mul <- decompose(train_ES, type = 'multiplicative')
plot(fit_mul)
```

## 1.simple exponential smoothing
assumes no trend, no seasonality
```{r}
ses_forecast <- ses(train_ES, h = 12)
plot(ses_forecast)
```
```{r}
summary(ses_forecast)
```

# 2. holt linear trend
assumes trend, no seasonality
```{r}
holt_forecast <- holt(train_ES, h = 12)
plot(holt_forecast)
```
```{r}
summary(holt_forecast)
```
# 3. exponential trend method
```{r}
exponential_trend_forecast <- holt(train_ES, h = 12, exponential = TRUE)
plot(exponential_trend_forecast)
```


# 4.triple exponential smoothing (holt-winters)
assumes trend, seasonality
gamma is high, indicating estimate of the seasonal component at current time point is based upon very recent observations
```{r}
holtwinters_forecast <- HoltWinters(train_ES, seasonal = 'multiplicative')
holtwinters_forecast1 <- forecast(holtwinters_forecast, h = 12)
plot(holtwinters_forecast1)
```

```{r}
summary(holtwinters_forecast1)
```

```{r}
holtwinters_forecast_ad <- HoltWinters(train_ES, seasonal = 'additive')
holtwinters_forecast2 <- forecast(holtwinters_forecast_ad, h = 12)
plot(holtwinters_forecast2)
```

```{r}
summary(holtwinters_forecast2)
```

# Visualizations of test vs. forecasted
```{r}
autoplot(train_ES) + 
  autolayer(test_ES, series = 'actual test data') + 
  autolayer(ses_forecast$mean, series = 'Simple Exponential Smoothing')
```

```{r}
autoplot(train_ES) + 
  autolayer(test_ES, series = 'actual test data') + 
  autolayer(holt_forecast$mean, series = 'holt linear trend')
```
```{r}
autoplot(train_ES) + 
  autolayer(test_ES, series = 'actual test data') + 
  autolayer(exponential_trend_forecast$mean, series = 'exponential trend')
```


```{r}
autoplot(train_ES) + 
  autolayer(test_ES, series = 'actual test data') + 
  autolayer(holtwinters_forecast1$mean, series = 'Triple Exponential Smoothing multiplicative (Holt-Winters)')
```
```{r}
autoplot(train_ES) + 
  autolayer(test_ES, series = 'actual test data') + 
  autolayer(holtwinters_forecast2$mean, series = 'Triple Exponential Smoothing additive (Holt-Winters)')
```


```{r}
autoplot(exp(test_ES), series = 'actual test data') + 
  autolayer(exp(ses_forecast$mean), series = 'Simple Exponential Smoothing') + 
  autolayer(exp(holt_forecast$mean), series = 'Holt Linear Trend') +
  autolayer(exp(exponential_trend_forecast$mean), series = 'Exponential Trend') +
  autolayer(exp(holtwinters_forecast1$mean), series = 'Holtwinters multiplicative')+
  autolayer(exp(holtwinters_forecast2$mean), series = 'Holtwinters additive')
```
# Metrics

```{r}
mape_ses <- mape(exp(test_ES), exp(ses_forecast$mean))
mape_holt <- mape(exp(test_ES), exp(holt_forecast$mean))
mape_exponential <- mape(exp(test_ES), exp(exponential_trend_forecast$mean))
mape_hw_m <- mape(exp(test_ES), exp(holtwinters_forecast1$mean))
mape_hw_a <- mape(exp(test_ES), exp(holtwinters_forecast2$mean))


mse_ses <- mse(exp(test_ES),exp(ses_forecast$mean))
mse_holt <- mse(exp(test_ES), exp(holt_forecast$mean))
mse_exponential <- mse(exp(test_ES), exp(exponential_trend_forecast$mean))
mse_hw_m <- mse(exp(test_ES), exp(holtwinters_forecast1$mean))
mse_hw_a <- mse(exp(test_ES), exp(holtwinters_forecast2$mean))


MAPE=c(mape_ses,mape_holt, mape_exponential, mape_hw_m, mape_hw_a)
MSE = c(mse_ses,mse_holt,mse_exponential, mse_hw_m,mse_hw_a)

model_name = c('Simple Exponential Smoothing','Holt Linear Trend','Exponential Trend','Holt-Winters Multiplicative', 'Holt-Winters Additive')

results <- data.frame(model = model_name, MAPE = MAPE, MSE = MSE)
results
```


# 3. Regression and Regression with ARMA errors
```{r}
lm <- tslm(train ~ train_pm10 + train_so2 + train_co + train_no2 + train_temp + train_o3 + train_wspm)
summary(lm)
```

```{r}
lm_reduced_1 <- tslm(train ~ train_pm10 + train_co + train_no2 + train_wspm)
summary(lm_reduced_1)

lm_reduced_2 <- tslm(train ~ train_pm10 + train_co)
summary(lm_reduced_2)
```

```{r}
checkresiduals(lm_reduced_1)
checkresiduals(lm_reduced_2)
```

```{r}
m_arima_1 <- auto.arima(y = train, xreg = cbind(pm10 = train_pm10, co = train_co, no2 = train_no2, wspm = train_wspm), seasonal = T)
summary(m_arima_1)
m_arima_2 <- auto.arima(y = train, xreg = cbind(pm10 = train_pm10, co = train_co), seasonal = T)
summary(m_arima_2)

m_arima_1_log <- auto.arima(y = train, lambda = 0, xreg = cbind(pm10 = train_pm10, co = train_co, no2 = train_no2, wspm = train_wspm), seasonal = T)
summary(m_arima_1_log)
m_arima_2_log <- auto.arima(y = train, lambda = 0, xreg = cbind(pm10 = train_pm10, co = train_co), seasonal = T)
summary(m_arima_2_log)
```

```{r}
checkresiduals(m_arima_1)
checkresiduals(m_arima_2)
```

```{r}
# If we know other variables:
forecast_arima1 <- forecast(m_arima_1, h = 13, xreg = cbind(pm10 = test_pm10, co = test_co, no2 = test_no2, wspm = test_wspm))
forecast_arima2 <- forecast(m_arima_2, h = 13, xreg = cbind(pm10 = test_pm10, co = test_co))
plot(forecast_arima1)
lines(test, type = 'l', col = 'red')
plot(forecast_arima2)
lines(test, type = 'l', col = 'red')
legend("topleft", legend=c("Predicted","Actual"), col=c("blue","red"), lty=1, pch = 1, cex = 0.75)
```


```{r}
# if we don't
# we use snaive and arima to predict xreg variables
m_pm10_arima <- auto.arima(train_pm10, seasonal= T)
m_co_arima <- auto.arima(train_co, seasonal= T)
m_no2_arima <- auto.arima(train_no2, seasonal= T)
m_wspm_arima <- auto.arima(train_wspm, seasonal= T)

forecast_arima1 <- forecast(m_arima_1, h = 12, 
                            xreg = cbind(pm10 = forecast(snaive(train_pm10, h = 12))$mean, 
                                         co = forecast(snaive(train_co, h = 12))$mean, 
                                         no2 = forecast(snaive(train_no2, h = 12))$mean, 
                                         wspm = forecast(snaive(train_wspm, h = 12))$mean))
plot(forecast_arima1)
lines(test, type = 'l', col = 'red')
legend("topleft", legend=c("Predicted","Actual"), col=c("blue","red"), lty=1, pch = 1, cex = 0.75)

forecast_arima2 <- forecast(m_arima_1, h = 12, 
                            xreg = cbind(pm10 = forecast(m_pm10_arima, h = 12)$mean, 
                                         co = forecast(m_co_arima, h = 12)$mean, 
                                         no2 = forecast(m_no2_arima, h = 12)$mean, 
                                         wspm = forecast(m_wspm_arima, h = 12)$mean))
plot(forecast_arima2)
lines(test, type = 'l', col = 'red')
legend("topleft", legend=c("Predicted","Actual"), col=c("blue","red"), lty=1, pch = 1, cex = 0.75)

forecast_arima3 <- forecast(m_arima_2, h = 12, 
                            xreg = cbind(pm10 = forecast(snaive(train_pm10, h = 12))$mean, 
                                         co = forecast(snaive(train_co, h = 12))$mean))
plot(forecast_arima3)
lines(test, type = 'l', col = 'red')
legend("topleft", legend=c("Predicted","Actual"), col=c("blue","red"), lty=1, pch = 1, cex = 0.75)

forecast_arima4 <- forecast(m_arima_2, h = 12, 
                            xreg = cbind(pm10 = forecast(m_pm10_arima, h = 12)$mean, 
                                         co = forecast(m_co_arima, h = 12)$mean))
plot(forecast_arima4)
lines(test, type = 'l', col = 'red')
legend("topleft", legend=c("Predicted","Actual"), col=c("blue","red"), lty=1, pch = 1, cex = 0.75)


# MAPE
mape1 <- mean(abs(test - forecast_arima1$mean) / test)
# MSE
mse1 <- mean((test - forecast_arima1$mean)^2)

# MAPE
mape2 <- mean(abs(test - forecast_arima2$mean) / test)
# MSE
mse2 <- mean((test - forecast_arima2$mean)^2)

# MAPE
mape3 <- mean(abs(test - forecast_arima3$mean) / test)
# MSE
mse3 <- mean((test - forecast_arima3$mean)^2)

# MAPE
mape4 <- mean(abs(test - forecast_arima4$mean) / test)
# MSE
mse4 <- mean((test - forecast_arima4$mean)^2)


cbind(mape1, mse1, mape2, mse2, mape3, mse3, mape4, mse4)
```

```{r}
autoplot(test, series = 'Test') + 
  autolayer(forecast_arima1$mean, series = "Arima_4Xreg_SNaive") +
  autolayer(forecast_arima2$mean, series = "Arima_4Xreg_Arima") +
  autolayer(forecast_arima3$mean, series = "Arima_2Xreg_SNaive") +
  autolayer(forecast_arima4$mean, series = "Arima_2Xreg_Arima")
```
```{r}
model_name = c('Arima with 4 Xreg predicted by Seasonal Naive','Arima with 4 Xreg predicted by Seasonal Arima','Arima with 2 Xreg predicted by Seasonal Naive','Arima with 2 Xreg predicted by Seasonal Arima')

results <- data.frame(model = model_name, MAPE = c(mape1, mape2, mape3, mape4), MSE = c(mse1, mse2, mse3, mse4), AICc = c(m_arima_1$aicc, m_arima_1$aicc, m_arima_2$aicc, m_arima_2$aicc))
results
```


## e. Cross Validation


```{r}
k <- 140 # minimum data length for fitting a model
n <- length(PM2.5_week) # Number of data points

p <- 52 ### Period
H <- 12 # Forecast Horizon
```


```{r warning=FALSE}
# Arima and Arima on Error
st <- tsp(PM2.5_week)[1]+(k-2)/p #  gives the start time in time units,

mse_1 <- matrix(NA,n-k,H)
mse_2 <- matrix(NA,n-k,H)
mse_3 <- matrix(NA,n-k,H)
mse_4 <- matrix(NA,n-k,H)
mse_5 <- matrix(NA,n-k,H)
mse_6 <- matrix(NA,n-k,H)
mse_7 <- matrix(NA,n-k,H)
mse_8 <- matrix(NA,n-k,H)
mse_9 <- matrix(NA,n-k,H)
mse_10 <- matrix(NA,n-k,H)


aicc_1 <- matrix(NA,n-k,1)
aicc_2 <- matrix(NA,n-k,1)
aicc_3 <- matrix(NA,n-k,1)
aicc_4 <- matrix(NA,n-k,1)
aicc_5 <- matrix(NA,n-k,1)
aicc_6 <- matrix(NA,n-k,1)
aicc_7 <- matrix(NA,n-k,1)
aicc_8 <- matrix(NA,n-k,1)
aicc_9 <- matrix(NA,n-k,1)
aicc_10 <- matrix(NA,n-k,1)


for(i in 1:(n-k))
{
  print(paste0(i, '/', n-k))
  ### One Month rolling forecasting
  # Expanding Window 
  train_1 <- window(PM2.5_week, end=st + i/p)  ## Window Length: k+i
  train_pm10_1 <- window(PM10_week, end=st + i/p)  ## Window Length: k+i
  train_no2_1 <- window(NO2_week, end=st + i/p)  ## Window Length: k+i
  train_co_1 <- window(CO_week, end=st + i/p)  ## Window Length: k+i
  train_wspm_1 <- window(WSPM_week, end=st + i/p)  ## Window Length: k+i

  # Sliding Window - keep the training window of fixed length. 
  # The training set always consists of k observations.
  train_2 <- window(PM2.5_week, start=st+(i-k+1)/p, end=st+i/p) ## Window Length: k
  train_pm10_2 <- window(PM10_week, start=st+(i-k+1)/p, end=st+i/p) ## Window Length: k
  train_no2_2 <- window(NO2_week, start=st+(i-k+1)/p, end=st+i/p) ## Window Length: k
  train_co_2 <- window(CO_week, start=st+(i-k+1)/p, end=st+i/p) ## Window Length: k
  train_wspm_2 <- window(WSPM_week, start=st+(i-k+1)/p, end=st+i/p) ## Window Length: k
  
  test <- window(PM2.5_week, start=st + (i+1)/p, end=st + (i+H)/p) ## Window Length: H

  m4_1 <- auto.arima(train_1,lambda = 0,seasonal = TRUE)
  m6_1 <- auto.arima(train_1,lambda = 0,seasonal = TRUE,D=1)
  m8_1 <- auto.arima(train_1,seasonal = TRUE)
  
  m4_2 <- auto.arima(train_2,lambda = 0,seasonal = TRUE)
  m6_2 <- auto.arima(train_2,lambda = 0,seasonal = TRUE,D=1)
  m8_2 <- auto.arima(train_2,seasonal = TRUE)

  m_arima_1 <- auto.arima(y = train_1, xreg = cbind(pm10 = train_pm10_1, co = train_co_1, no2 = train_no2_1, wspm = train_wspm_1), seasonal = T)
  
  m_arima_2 <- auto.arima(y = train_2, xreg = cbind(pm10 = train_pm10_2, co = train_co_2, no2 = train_no2_2, wspm = train_wspm_2), seasonal = T)

  m_arima_3 <- auto.arima(y = train_1, xreg = cbind(pm10 = train_pm10_1, co = train_co_1), seasonal = T)

  m_arima_4 <- auto.arima(y = train_2, xreg = cbind(pm10 = train_pm10_2, co = train_co_2), seasonal = T)
  
  m_pm10_arima_1 <- auto.arima(train_pm10_1, seasonal= T)
  m_co_arima_1 <- auto.arima(train_co_1, seasonal= T)
  m_no2_arima_1 <- auto.arima(train_no2_1, seasonal= T)
  m_wspm_arima_1 <- auto.arima(train_wspm_1, seasonal= T)
 
  m_pm10_arima_2 <- auto.arima(train_pm10_2, seasonal= T)
  m_co_arima_2 <- auto.arima(train_co_2, seasonal= T)
  m_no2_arima_2 <- auto.arima(train_no2_2, seasonal= T)
  m_wspm_arima_2 <- auto.arima(train_wspm_2, seasonal= T)
  
  fcast_1 <- forecast(m_arima_1, h = H, 
                            xreg = cbind(pm10 = forecast(m_pm10_arima_1, h = H)$mean, 
                                         co = forecast(m_co_arima_1, h = H)$mean, 
                                         no2 = forecast(m_no2_arima_1, h = H)$mean, 
                                         wspm = forecast(m_wspm_arima_1, h = H)$mean))

  fcast_2 <- forecast(m_arima_2, h = H, 
                            xreg = cbind(pm10 = forecast(m_pm10_arima_2, h = H)$mean, 
                                         co = forecast(m_co_arima_2, h = H)$mean, 
                                         no2 = forecast(m_no2_arima_2, h = H)$mean, 
                                         wspm = forecast(m_wspm_arima_2, h = H)$mean))

  fcast_3 <- forecast(m_arima_3, h = H, 
                            xreg = cbind(pm10 = forecast(m_pm10_arima_1, h = H)$mean, 
                                         co = forecast(m_co_arima_1, h = H)$mean))

  fcast_4 <- forecast(m_arima_4, h = H, 
                            xreg = cbind(pm10 = forecast(m_pm10_arima_2, h = H)$mean, 
                                         co = forecast(m_co_arima_2, h = H)$mean))

  fcast_5 <- forecast(m4_1, h = H)
  
  fcast_6 <- forecast(m4_2, h = H)
  
  fcast_7 <- forecast(m6_1, h = H)
  
  fcast_8 <- forecast(m6_2, h = H)

  fcast_9 <- forecast(m8_1, h = H)
  
  fcast_10 <- forecast(m8_2, h = H)

  mse_1[i,1:length(test)] <- (fcast_1[['mean']]-test)^2
  mse_2[i,1:length(test)] <- (fcast_2[['mean']]-test)^2
  mse_3[i,1:length(test)] <- (fcast_3[['mean']]-test)^2
  mse_4[i,1:length(test)] <- (fcast_4[['mean']]-test)^2
  mse_5[i,1:length(test)] <- (fcast_5[['mean']]-test)^2
  mse_6[i,1:length(test)] <- (fcast_6[['mean']]-test)^2
  mse_7[i,1:length(test)] <- (fcast_7[['mean']]-test)^2
  mse_8[i,1:length(test)] <- (fcast_8[['mean']]-test)^2
  mse_9[i,1:length(test)] <- (fcast_9[['mean']]-test)^2
  mse_10[i,1:length(test)] <- (fcast_10[['mean']]-test)^2

  
  aicc_1[i,1] <- m_arima_1$aicc
  aicc_2[i,1] <- m_arima_2$aicc
  aicc_3[i,1] <- m_arima_3$aicc
  aicc_4[i,1] <- m_arima_4$aicc
  aicc_5[i,1] <- m4_1$aicc
  aicc_6[i,1] <- m4_2$aicc
  aicc_7[i,1] <- m6_1$aicc
  aicc_8[i,1] <- m6_2$aicc
  aicc_9[i,1] <- m8_1$aicc
  aicc_10[i,1] <- m8_2$aicc
}
```



```{r warning=FALSE}
# Exponential Smoothing
st <- tsp(PM2.5_ES)[1]+(k-2)/p #  gives the start time in time units,

mse_11 <- matrix(NA,n-k,H)
mse_12 <- matrix(NA,n-k,H)

aicc_11 <- matrix(NA,n-k,1)
aicc_12 <- matrix(NA,n-k,1)

for(i in 1:(n-k))
{
  print(paste0(i, '/', n-k))
  ### One Month rolling forecasting
  # Expanding Window 
  train_ES_1 <- window(PM2.5_ES, end=st + i/p)  ## Window Length: k+i

  # Sliding Window - keep the training window of fixed length. 
  # The training set always consists of k observations.
  train_ES_2 <- window(PM2.5_ES, start=st+(i-k+1)/p, end=st+i/p) ## Window Length: k

  test_ES <- exp(window(PM2.5_ES, start=st + (i+1)/p, end=st + (i+H)/p)) ## Window Length: H

  m_HW_1 <- HoltWinters(train_ES_1, seasonal = 'multiplicative')
  m_HW_2 <- HoltWinters(train_ES_2, seasonal = 'multiplicative')

  fcast_11 <- forecast(m_HW_1, h = H)
  fcast_12 <- forecast(m_HW_2, h = H)

  mse_11[i,1:length(test_ES)] <- (exp(fcast_11[['mean']])-test_ES)^2
  mse_12[i,1:length(test_ES)] <- (exp(fcast_12[['mean']])-test_ES)^2
}
```

```{r}
# log arima with regresson error
st <- tsp(PM2.5_week)[1]+(k-2)/p #  gives the start time in time units,

mse_13 <- matrix(NA,n-k,H)
mse_14 <- matrix(NA,n-k,H)
mse_15 <- matrix(NA,n-k,H)
mse_16 <- matrix(NA,n-k,H)

aicc_13 <- matrix(NA,n-k,1)
aicc_14 <- matrix(NA,n-k,1)
aicc_15 <- matrix(NA,n-k,1)
aicc_16 <- matrix(NA,n-k,1)

for(i in 1:(n-k))
{
  print(paste0(i, '/', n-k))
  ### One Month rolling forecasting
  # Expanding Window 
  train_1 <- window(PM2.5_week, end=st + i/p)  ## Window Length: k+i
  train_pm10_1 <- window(PM10_week, end=st + i/p)  ## Window Length: k+i
  train_no2_1 <- window(NO2_week, end=st + i/p)  ## Window Length: k+i
  train_co_1 <- window(CO_week, end=st + i/p)  ## Window Length: k+i
  train_wspm_1 <- window(WSPM_week, end=st + i/p)  ## Window Length: k+i

  # Sliding Window - keep the training window of fixed length. 
  # The training set always consists of k observations.
  train_2 <- window(PM2.5_week, start=st+(i-k+1)/p, end=st+i/p) ## Window Length: k
  train_pm10_2 <- window(PM10_week, start=st+(i-k+1)/p, end=st+i/p) ## Window Length: k
  train_no2_2 <- window(NO2_week, start=st+(i-k+1)/p, end=st+i/p) ## Window Length: k
  train_co_2 <- window(CO_week, start=st+(i-k+1)/p, end=st+i/p) ## Window Length: k
  train_wspm_2 <- window(WSPM_week, start=st+(i-k+1)/p, end=st+i/p) ## Window Length: k
  
  test <- window(PM2.5_week, start=st + (i+1)/p, end=st + (i+H)/p) ## Window Length: H

  m_arima_1 <- auto.arima(y = train_1, xreg = cbind(pm10 = train_pm10_1, co = train_co_1, no2 = train_no2_1, wspm = train_wspm_1), seasonal = T, lambda = 0)
  
  m_arima_2 <- auto.arima(y = train_2, xreg = cbind(pm10 = train_pm10_2, co = train_co_2, no2 = train_no2_2, wspm = train_wspm_2), seasonal = T, lambda = 0)

  m_arima_3 <- auto.arima(y = train_1, xreg = cbind(pm10 = train_pm10_1, co = train_co_1), seasonal = T, lambda = 0)

  m_arima_4 <- auto.arima(y = train_2, xreg = cbind(pm10 = train_pm10_2, co = train_co_2), seasonal = T, lambda = 0)
  
  m_pm10_arima_1 <- auto.arima(train_pm10_1, seasonal= T)
  m_co_arima_1 <- auto.arima(train_co_1, seasonal= T)
  m_no2_arima_1 <- auto.arima(train_no2_1, seasonal= T)
  m_wspm_arima_1 <- auto.arima(train_wspm_1, seasonal= T)
 
  m_pm10_arima_2 <- auto.arima(train_pm10_2, seasonal= T)
  m_co_arima_2 <- auto.arima(train_co_2, seasonal= T)
  m_no2_arima_2 <- auto.arima(train_no2_2, seasonal= T)
  m_wspm_arima_2 <- auto.arima(train_wspm_2, seasonal= T)
  
  fcast_1 <- forecast(m_arima_1, h = H, 
                            xreg = cbind(pm10 = forecast(m_pm10_arima_1, h = H)$mean, 
                                         co = forecast(m_co_arima_1, h = H)$mean, 
                                         no2 = forecast(m_no2_arima_1, h = H)$mean, 
                                         wspm = forecast(m_wspm_arima_1, h = H)$mean))

  fcast_2 <- forecast(m_arima_2, h = H, 
                            xreg = cbind(pm10 = forecast(m_pm10_arima_2, h = H)$mean, 
                                         co = forecast(m_co_arima_2, h = H)$mean, 
                                         no2 = forecast(m_no2_arima_2, h = H)$mean, 
                                         wspm = forecast(m_wspm_arima_2, h = H)$mean))

  fcast_3 <- forecast(m_arima_3, h = H, 
                            xreg = cbind(pm10 = forecast(m_pm10_arima_1, h = H)$mean, 
                                         co = forecast(m_co_arima_1, h = H)$mean))

  fcast_4 <- forecast(m_arima_4, h = H,
                            xreg = cbind(pm10 = forecast(m_pm10_arima_2, h = H)$mean, 
                                         co = forecast(m_co_arima_2, h = H)$mean))

  mse_13[i,1:length(test)] <- (fcast_1[['mean']]-test)^2
  mse_14[i,1:length(test)] <- (fcast_2[['mean']]-test)^2
  mse_15[i,1:length(test)] <- (fcast_3[['mean']]-test)^2
  mse_16[i,1:length(test)] <- (fcast_4[['mean']]-test)^2
 
  aicc_13[i,1] <- m_arima_1$aicc
  aicc_14[i,1] <- m_arima_2$aicc
  aicc_15[i,1] <- m_arima_3$aicc
  aicc_16[i,1] <- m_arima_4$aicc
}
```


```{r}
# Expanding MSE
plot(1:12, colMeans(mse_1,na.rm=TRUE), type="l",col=1,xlab="horizon", ylab="MSE", main = "MSE of different models and CV method", ylim = c(-0, 7000))
lines(1:12, colMeans(mse_3,na.rm=TRUE), type="l",col=2)
lines(1:12, colMeans(mse_5,na.rm=TRUE), type="l",col=3)
lines(1:12, colMeans(mse_7,na.rm=TRUE), type="l",col=4)
lines(1:12, colMeans(mse_9,na.rm=TRUE), type="l",col=5)
lines(1:12, colMeans(mse_11,na.rm=TRUE), type="l",col=6)
lines(1:12, colMeans(mse_13,na.rm=TRUE), type="l",col=7)
lines(1:12, colMeans(mse_15,na.rm=TRUE), type="l",col=8)
legend("topright",legend=c("Arima_4Xreg - Expanding Window","Arima_2Xreg - Expanding Window", "Seasonal Log Arima - Expanding Window", "Seasonal Log Arima with D=1 - Expanding Window", "Seasonal Arima- Expanding Window", "HoltWinter Multiplicative - Expanding Window", 'Log Arima_4Xreg - Expanding Window', 'Log Arima_2Xreg - Expanding Window'),col=1:8,lty=1)
```

```{r}
# Sliding MSE
plot(1:12, colMeans(mse_2,na.rm=TRUE), type="l",col=1,xlab="horizon", ylab="MSE", main = "MSE of different models and CV method", ylim = c(0, 12000))
lines(1:12, colMeans(mse_4,na.rm=TRUE), type="l",col=2)
lines(1:12, colMeans(mse_6,na.rm=TRUE), type="l",col=3)
lines(1:12, colMeans(mse_8,na.rm=TRUE), type="l",col=4)
lines(1:12, colMeans(mse_10,na.rm=TRUE), type="l",col=5)
lines(1:12, colMeans(mse_12,na.rm=TRUE), type="l",col=6)
lines(1:12, colMeans(mse_14,na.rm=TRUE), type="l",col=7)
lines(1:12, colMeans(mse_16,na.rm=TRUE), type="l",col=8)
legend("topright",legend=c("Arima_4Xreg - Sliding Window","Arima_2Xreg - Sliding Window", "Seasonal Log Arima - Sliding Window", "Seasonal Log Arima with D=1 - Sliding Window", "Seasonal Arima- Sliding Window", "HoltWinter Multiplicative - Sliding Window", 'Log Arima_4Xreg - Sliding Window', 'Log Arima_2Xreg - Sliding Window'),col=1:8,lty=1)

```


```{r}
# Expanding AICc
plot(1:69, aicc_1, type="l",col=1,xlab="horizon", ylab="AICc", main = "AICc of different models and CV method", ylim = c(0, 4000))
lines(1:69, aicc_3, type="l",col=2)
lines(1:69, aicc_5, type="l",col=3)
lines(1:69, aicc_7, type="l",col=4)
lines(1:69, aicc_9, type="l",col=5)
lines(1:69, aicc_13, type="l",col=6)
lines(1:69, aicc_15, type="l",col=7)
legend("topright",legend=c("Arima_4Xreg - Expanding Window","Arima_2Xreg - Expanding Window", "Seasonal Log Arima - Expanding Window", "Seasonal Log Arima with D=1 - Expanding Window", "Seasonal Arima- Expanding Window", 'Log Arima_4Xreg - Expanding Window', 'Log Arima_2Xreg - Expanding Window'),col=1:7,lty=1)
```

```{r}
# Expanding AICc
plot(1:69, aicc_2, type="l",col=1,xlab="horizon", ylab="AICc", main = "AICc of different models and CV method", ylim = c(0, 3000))
lines(1:69, aicc_4, type="l",col=2)
lines(1:69, aicc_6, type="l",col=3)
lines(1:69, aicc_8, type="l",col=4)
lines(1:69, aicc_10, type="l",col=5)
lines(1:69, aicc_14, type="l",col=6)
lines(1:69, aicc_16, type="l",col=7)
legend("topright",legend=c("Arima_4Xreg - Sliding Window","Arima_2Xreg - Sliding Window", "Seasonal Log Arima - Sliding Window", "Seasonal Log Arima with D=1 - Sliding Window", "Seasonal Arima- Sliding Window", 'Log Arima_4Xreg - Sliding Window', 'Log Arima_2Xreg - Sliding Window'),col=1:7,lty=1)
```






